Literature Review

### 2019-02-25 litreview.Rmd
update
updates

#Overview
This page links out to sub-pages that describe various background topics. Follow the links for details.

Description: https://adanieljohnson.github.io/default_website/pagename.html

Technical Writing Training

Text Classification Strategies

>>>>

#Overview
The supporting literature for this project is broad and convoluted. Rather than try to compress it to a single page, I have provided links out to sub-pages that describe various background topics. Follow the links for details.

Fundamental Principles and Practices of Technical Writing Training:  https://adanieljohnson.github.io/default_website/pagename.html

Primer on Text Classification Strategies:  https://adanieljohnson.github.io/default_website/Text_classifier_models.html
